\documentclass{resume}
\usepackage{url}
\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Tony Lijo Jose}
% ------ Address --------------------------------------------------------

\address{Development Engineer\\
  K7 Computing Private Limited\\
  Chennai,TamilNadu\\
  {\em Ph:} (+91)-94-4449-8808}{
  {\em email:} \mbox{\small\tt mail@tonylijo.in}\\
  {\em github:} \mbox{\small\tt \url{github.com/tonylijo}}\\
  {\em linkedin:} \mbox{\small\tt \url{linkedin.com/in/tonylijo}}}

\begin{document}
\maketitle

% ------- Education ---------------------------------------------------

\begin{category}{Education}
  \citem{B-Tech in Computer Science \& Engineering} \hfill \textbf{2007 -- 2011}
  \citemnobullet Government Engineering College Palakkad, Kerala.
  \citem{Higher Secondary Education in Science} \hfill \textbf{2003 -- 2005}
  \citemnobullet Imigration Jubilee Memorial Higher secondary school Kottiyoor, Kerala.
\end{category}

% --------- Research ----------------------------------------------------

\begin{category}{Research interests}
  \citemnobullet Linux System programming,AVR/ARM Development,NoSQL databases, application development for Mac OSX and Linux ,development on Raspberry Pi.
\end{category}

\begin{category}{Technical Skills}
  \citembullet {\it Operating Systems}: GNU/Linux, Mac OSX.
  \citembullet {\it Programming Languages}:C(proficient),C++, Objective C, Python(proficient).
  \citembullet {\it Databases}: MySQL, Riak.
  \citembullet {\it Tools}:  RabbitMQ, HAProxy, Nginx.
  \citembullet {\it Version Control}: Git, Subversion, Mercurial.
  \citembullet {\it Cloud Platforms}:  Amazon EC2, Amazon S3.
  \citembullet {\it Specialities}: C , C++ , Python, Cloud Computing, Scalable design, Big Data, Commandline 
  tools, NoSQL databases, Virtualization, API design, Web services, Automation \& deployment, 
  Desktop applications, Shell scripting, Userspace filesystems, Microframeworks, System integration,MicroControllers AVR,ARM.
\end{category}

% -------- Work experience --------------------------------------------

\begin{category}{Work experience}
  \citem{K7 Computing, Chennai}
  \citemnobullet \textbf{{Development Engineer} \hfill Nov 2012 -- present}
  \citemnobullet Working as part of a team responsible for Developing Products Based on Cloud ,Hosting, and Security Domain
  \begin{itemize}

  \item {{\bfseries K7Tracker} \\
  K7 Tracker is an invisible software security application that traces the location of missing
  laptops for recovery. It is a light weight application that will help you track and find your
  laptop if it ever gets stolen. K7 Tracker provides a method for mitigating this risk. This
  tracking system send, over the Internet, updates regarding the current location of the device
  to a remotely administered repository. If the device is lost or stolen, but maintains Internet
  connectivity and unmodified software, the tracking system can keep tabs on the current
  whereabouts of the device. This data could prove invaluable when the appropriate authorities attempt to recover the device\\
  \url{http://k7tracker.com}\\
  {\it Role:}\\
  Development of Server, Linux and Mac Agents\\
  }

  \item {{\bfseries StackIron} \\
  A platform that lets hosting providers setup a Cloud VPS/IaaS business in mere hours. 
  Includes support for industry leading, hosting focused billing systems. 
  StackIron is a highly scalable platform with VPS failover, management server high availability,
  support for multiple hypervisor technologies, etc.\\
  \url{http://www.youtube.com/watch?v=yyT9DkHpnA4}\\
  {\it Role:}\\
  Development of strackiron Driver for scaleInfra\\
  } 

  \item{{\bfseries EggPlugg} \\
  A personal cloud appliance/hardware that lets you access your data no matter where you 
  are and also let you share and monitor your shares. What's best: It looks like a real egg! 
  Personal cloud storage that let you keep your data with you and you don't have to spend more to store more. 
  \url{http://www.youtube.com/watch?v=JR4O_AgsM2c}\\
  {\it Role:}\\
  Configuring and Maintaining the Eggplugg device software and hardware\\
  }

  \item{{\bfseries K7 Linux Antivirus}\\
  A Linux Version of K7 antivirus was implemented. 
  This antivirus could scan for malware in computer ,It also could update
  the latest malware database . This antivirus was used in the enterprise antivirus
  product to find the malwares in linux platform.
  {\it Role:}\\
  Integrating K7AV engine into linux with development of multiple components required for AV\\
  }

  \item {{\bfseries Unified Thread Management}\\
  A Product which could do intrusion detection and virus analysis.
  This looks like a packet router device which will help to find the intruders.
  It also scans the packets realtime with the help of AV signatures and finds if 
  the packet is containing virus content!\\
  {\it Role:}
  Research and Development\\
  wrote Kernel drivers to sniff packets from kernel space , wrote char drivers to 
  update signatures from userspace to kernel space , wrote char drivers to control
  the scanning from userspace.\\
  }

  \end{itemize}
  \citem{Inxs Technologies, Chennai} 
  \citemnobullet {\textbf{Software Engineer} \hfill Jan 2012 -- Nov 2012}
  \citemnobullet {Actively involved in the design and development of a High performance Trading platforms,
                  Was a part of marketsimplifieds platform team which was responsible for integrating 
                  various brokers into marketsimplified's single platfrom and protocol.I was actively involved
                  in devoloping an Analytics product which could derive a score for a stock based on its 
                  technical strength \\}

\end{category}
%--------- Personal Project ---------------------------------------
\begin{category}{Personal Projects\\}
    \citemnobullet{{Design of a toy Python virtual machine in C} \\
    \url{github: https://github.com/tonylijo/micro­pvm}}
    \citemnobullet{{Designed a small task switcher for arm Lpc2148 processor}\\
        \url{http://blog.tonylijo.in/2011/11/task­switching­in­msp430.html}\\
        \url{https://github.com/tonylijo/MSP430­TASK­SWITCHER}\\
        \url{https://github.com/tonylijo/arm­os}}
    \citemnobullet{{Lispy – A Lisp implementation in the JVM language Groovy.\\
           Peter Norvig had written a tiny Lisp interpreter in Python. I rewrotethe lisp 
           intrepretor  in Groovy } \\
       \url{https://github.com/tonylijo/lispy}}
    \citemnobullet{{Design of a FUSE version of ISO file system module.}\\
        \url{https://github.com/tonylijo/fuse­version­of­isofilesystem }}
    \citemnobullet{{Design of ext2 file system simulator.}\\
        \url{https://github.com/tonylijo/ext2filesystem}}
    \citemnobullet{{Design of an obstacle avoiding robot.}\\
        \url{ https://github.com/tonylijo/Obstrucle­}}
    \citemnobullet{{Design of a Wireless LED dot matrix display.}\\
        \url{ https://github.com/tonylijo/led­dot­matrix­display }}
    \citemnobullet{{A simple data compression tool
            Implemented a simple data compression tool in Python
            based on huffman coding algorithm.}\\
        \url{https://github.com/tonylijo/huffman­coding}}
    \citemnobullet{{Design of a Hello world Bootloader.}}
    \citemnobullet{{Linux Kernel parallel port driver}}
\end{category}
% -------- Awards & Honours ---------------------------------------

\begin{category}{Awards \&\\ Honours}
  \citem{``Best Project''}, {\em Computer Science, Government Engineering College Sreekrishnapuram}. \hfill \textbf{2012}
  \citem{``Founder of Foss Cell''}, {\em I was the founder of Foss Cell GEC Sreekrishnapuram}.
  \citem{``Year Representative''}, {\em Was Elected as Year representative in College union election.}
\end{category}


% -------- Reference --------------------------------------------

\begin{category}{Reference}
  \citemnobullet \\
  \begin{tabular}{ll}Shuveb Hussain&Towfeeque Aalam\\
    Head, Cloud Computing&Development Manager, Cloud Computing\\
    K7 Computing Private Limited&K7 Computing Private Limited\\
    Chennai - 600041&Chennai - 600041\\
    Email: \mbox{\small\tt shuveb@gmail.com}&Email: \mbox{\small\tt taufiqaalam@gmail.com}\\
    Ph: (+91)-98-4038-0386&Ph: (+91)-95-0008-7617
  \end{tabular}
\end{category}
\end{document}
